Universal relations after GW170817

### 2018-11-28 paper/bin-love-after-gw170817.tex
commiting paper updates before pulling Katerinas update

\begin{table*}[ht!]
\centering
\caption{
Tabulated results for the estimated statistical errors on $\tilde{\Lambda}$ for the combined results of $N_A$ detections corresponding to the estimated upper, central, and lower limits of the binary NS merger detection rate $R$.
This is repeated for 5 future detector sensitivities: aLIGO, a\texttt{++}, Voyager, CE, and ET.
Below, $\rho^A_{\text{GW170817}}$ and $\sigma^A_{\text{GW170817}}$ correspond to the approximate SNR and $\sigma_{\tilde{\Lambda}}$ of GW170817 had it been observed by the future interferometer, and $\sigma^A_N$ corresponds to the final uncertainty on $\tilde{\Lambda}$ after $N_A$ detections on interferometer $A$.
It can be seen here that the statistical errors on $\tilde{\Lambda}$ become comparable with the systematics $\sigma_{\tilde{\Lambda}}=10$ from using improved binary Love relations from Voyager and on, indicating when it may be safe to utilize new universal relations.
Note the approximation for $\sigma^A_N$ under the O2 detector sensitivity is a poor estimate due to the small number of stacked events, $N_{\text{O2}}=1$, resulting in a high degree of randomness in population generation.
These results are shown graphically in Fig.~\ref{fig:stackedFisher}.
}\label{tab:variances}
\begin{tabular}{ c || c c c c c c c c} 
\hline
Detector ($A$) & $N_A (\text{Lower})$ & $N_A (\text{Central})$ & $N_A (\text{Upper})$ & $\rho^A_{\text{GW170817}}$ & $\sigma^A_{\text{GW170817}}$ & $\sigma^A_N (\text{Lower})$ & $\sigma^A_N (\text{Central})$ & $\sigma^A_N (\text{Large})$\\
\hline
\hline
O2 & $1$ & $1$ & $1$ & $32.40$ & $168.40$ & $558.18$ & $393.24$ & $279.44$\\
aLIGO & $23$ & $112$ & $344$ & $90.74$ & $75.44$ & $117.022$ & $42.89$ & $24.27$\\
a\texttt{++} & $208$ & $1004$ & $3091$ & $180.95$ & $31.55$ & $27.62$ & $13.36$ & $7.36$\\
Voyager & $3854$ & $1.85 \times 10^4$ & $5.71 \times 10^4$ & $428.89$ & $16.69$ & $8.57$ & $3.78$ & $2.16$\\
ET-D & $1.35\times 10^7$ & $6.50\times 10^7$ & $2.00\times 10^8$ & $2807.45$ & $6.26$ & $0.78$ & $0.35$ & $0.20$\\
CE & $3.98\times 10^5$ & $1.91\times 10^6$ & $5.89\times 10^6$ & $1398.03$ & $4.85$ & $0.34$ & $0.16$ & $0.10$\\
\hline
\end{tabular}
\end{table*}

>>>>

\begin{table*}[ht!]
\centering
\caption{
Tabulated results for the estimated statistical errors on $\tilde{\Lambda}$ for the combined results of $N_A$ detections corresponding to the estimated upper, central, and lower limits of the binary NS merger detection rate $R$.
This is repeated for 5 future detector sensitivities: aLIGO, a\texttt{++}, Voyager, CE, and ET.
Below, $\rho^A_{\text{GW170817}}$ and $\sigma^A_{\text{GW170817}}$ correspond to the approximate SNR and $\sigma_{\tilde{\Lambda}}$ of GW170817 had it been observed by the future interferometer, and $\sigma^A_N$ corresponds to the final uncertainty on $\tilde{\Lambda}$ after $N_A$ detections on interferometer $A$.
It can be seen here that the statistical errors on $\tilde{\Lambda}$ become comparable with the systematics $\sigma_{\tilde{\Lambda}}=10$ from using improved binary Love relations from Voyager and on, indicating when it may be safe to utilize new universal relations.
Note the approximation for $\sigma^A_N$ under the O2 detector sensitivity is a poor estimate due to the small number of stacked events, $N_{\text{O2}}=1$, resulting in a high degree of randomness in population generation.
These results are shown graphically in Fig.~\ref{fig:stackedFisher}.
}\label{tab:variances}
%\begin{tabular}{ c || c c c c c c c c} 
%\hline
%Detector ($A$) & $N_A (\text{Lower})$ & $N_A (\text{Central})$ & $N_A (\text{Upper})$ & $\rho^A_{\text{GW170817}}$ & $\sigma^A_{\text{GW170817}}$ & $\sigma^A_N (\text{Lower})$ & $\sigma^A_N (\text{Central})$ & $\sigma^A_N (\text{Upper})$\\
%\hline
%\hline
%O2 & $1$ & $1$ & $1$ & $32.40$ & $168.40$ & $558.18$ & $393.24$ & $279.44$\\
%aLIGO & $23$ & $112$ & $344$ & $90.74$ & $75.44$ & $117.022$ & $42.89$ & $24.27$\\
%a\texttt{++} & $208$ & $1004$ & $3091$              & $180.95$ & $31.55$ &               $27.62$ & $13.36$ & $7.36$\\
%Voyager & $3854$ & $1.85 \times 10^4$ & $5.71 \times 10^4$ &              $428.89$ & $16.69$              & $8.57$ & $3.78$ & $2.16$\\
%ET-D & $3.98\times 10^5$ & $1.91\times 10^6$ & $5.89\times 10^6$ &                  $2807.45$ & $6.26$ &               $0.78$ & $0.35$ & $0.20$\\
%CE & $1.35\times 10^7$ & $6.50\times 10^7$ & $2.00\times 10^8$ &                 $1398.03$ & $4.85$ &                 $0.34$ & $0.16$ & $0.10$\\
%\hline
%\end{tabular}
\begin{tabular}{|c|@{\extracolsep{4pt}}c@{\extracolsep{0pt}}|c|@{\extracolsep{4pt}}C{1.7cm}@{\extracolsep{-2pt}}|C{1.7cm}|@{\extracolsep{-2pt}}C{1.7cm}@{\extracolsep{2pt}}|c|@{\extracolsep{0pt}}c@{\extracolsep{0pt}}|c|}
\cline{1-1}\cline{2-3}\cline{4-9}
    \multicolumn{1}{|c|}{\bfseries Detectors (A)} & \multicolumn{2}{|c|}{\bfseries GW170817} & \multicolumn{6}{|c|}{\bfseries Multiple events} \\
\cline{1-1}\cline{2-3}\cline{4-9}
\noalign{\smallskip}
\cline{2-3}\cline{4-6}\cline{7-9}
\multicolumn{1}{c}{} & \multicolumn{1}{|c|}{} & \multicolumn{1}{c|}{} & \multicolumn{3}{|c|}{} & \multicolumn{3}{|c|}{}
\\[-1em]
\multicolumn{1}{c}{}  &  \multicolumn{1}{|c|}{\multirow{2}{*}{$\rho^A_{\text{GW170817}}$}}  &  \multirow{ 2}{*}{$\sigma^A_{\text{GW170817}}$}  &  \multicolumn{3}{|c|}{$N_A$}  &  \multicolumn{3}{|c|}{$\sigma^A_N$}  \\
\cline{4-6}\cline{7-9}
\multicolumn{1}{c}{}  &  \multicolumn{1}{|c|}{}  &  \multicolumn{1}{c|}{}  &  \multicolumn{1}{|c|}{Low}  &  \multicolumn{1}{c|}{Central} &  \multicolumn{1}{c|}{High}  & \multicolumn{1}{|c|}{Low}  &  \multicolumn{1}{c|}{Central} &  \multicolumn{1}{c|}{High}\\
\cline{2-3}\cline{4-6}\cline{7-9}
\noalign{\smallskip}
\noalign{\smallskip}
\cline{1-1}\cline{2-3}\cline{4-6}\cline{7-9}
 O2  & \multicolumn{1}{|c|}{$32.40$}  & $168.40$ &  \multicolumn{1}{|c|}{$1$} & $1$ & $1$ & \multicolumn{1}{|c|}{$558.18$} & $393.24$ & $279.44$\\
\cline{1-1}\cline{2-3}\cline{4-6}\cline{7-9}
 aLIGO  & \multicolumn{1}{|c|}{$90.74$}  & $75.44$ &  \multicolumn{1}{|c|}{$23$} & $112$ & $344$ & \multicolumn{1}{|c|}{$117.022$} & $42.89$ & $24.27$\\
\cline{1-1}\cline{2-3}\cline{4-6}\cline{7-9}
 a\texttt{++}  & \multicolumn{1}{|c|}{$180.95$}  & $31.55$ &  \multicolumn{1}{|c|}{$208$} & $1004$ & $3091$ & \multicolumn{1}{|c|}{$27.62$} & $13.36$ & $7.36$\\
\cline{1-1}\cline{2-3}\cline{4-6}\cline{7-9}

\multicolumn{1}{|c|}{} & \multicolumn{1}{|c|}{} & \multicolumn{1}{c|}{} & \multicolumn{1}{|c|}{} & \multicolumn{1}{c|}{} & \multicolumn{1}{c|}{} & \multicolumn{1}{|c|}{} & \multicolumn{1}{c|}{} & \multicolumn{1}{c|}{}
\\[-1em]

 Voyager  & \multicolumn{1}{|c|}{$428.89$}  & $16.69$ &  \multicolumn{1}{|c|}{$3854$} & $1.85 \times 10^4$ & $5.71 \times 10^4$ & \multicolumn{1}{|c|}{$8.57$} & $3.78$ & $2.16$\\
\cline{1-1}\cline{2-3}\cline{4-6}\cline{7-9}

\multicolumn{1}{|c|}{} & \multicolumn{1}{|c|}{} & \multicolumn{1}{c|}{} & \multicolumn{1}{|c|}{} & \multicolumn{1}{c|}{} & \multicolumn{1}{c|}{} & \multicolumn{1}{|c|}{} & \multicolumn{1}{c|}{} & \multicolumn{1}{c|}{}
\\[-1em]

 ET-D  & \multicolumn{1}{|c|}{$2807.45$}  & $6.26$ &  \multicolumn{1}{|c|}{$3.98 \times 10^5$} & $1.91 \times 10^6$ & $5.89 \times 10^6$ & \multicolumn{1}{|c|}{$0.78$} & $0.35$ & $0.20$\\
\cline{1-1}\cline{2-3}\cline{4-6}\cline{7-9}

\multicolumn{1}{|c|}{} & \multicolumn{1}{|c|}{} & \multicolumn{1}{c|}{} & \multicolumn{1}{|c|}{} & \multicolumn{1}{c|}{} & \multicolumn{1}{c|}{} & \multicolumn{1}{|c|}{} & \multicolumn{1}{c|}{} & \multicolumn{1}{c|}{}
\\[-1em]

 CE  & \multicolumn{1}{|c|}{$1398.03$}  & $4.85$ &  \multicolumn{1}{|c|}{$1.35 \times 10^7$} & $6.50 \times 10^7$ & $2.00 \times 10^8$ & \multicolumn{1}{|c|}{$0.34$} & $0.16$ & $0.10$\\
\cline{1-1}\cline{2-3}\cline{4-6}\cline{7-9}
\end{tabular}
\end{table*}
